Unfolding the City: Spatial Preference Based on Individual Demographic Characteristics

### 2020-01-18 ia/ia_vis_3d_final-yellow.tex
with yellow

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}

@@

Due to the multidimensional nature of demographic characteristics and the spatial diversity of movements, it is challenging to explore, analyze and express the relationship between these parameters. In recent decades, the power of visual analytics in urban problems has been recognized and developed well~\cite{wang2013visual, zeng2013visualizing}. The presence of social media applications fuels spatial analysis with rich semantic texts, so researchers can explore the thematic meaning of the movement behaviors, such as events~\cite{chen2017map} and topics~\cite{bosch2013scatterblogs2}. These works essentially contribute to deepening the contextual understanding of movement activities.  Some works dive deep and infer individual characteristics from social media profiles~\cite{peddinti2014internet} to better describe the semantics of movement behavior. However, due to the limited exposure of personal information, there is still a research gap between understanding the movement behavior and underlying characteristics of movers.
%The question of how to intuitively discover the relationship between spatial preference and multidimensional characteristics is worthy of further investigation.

@@

\subsection{Movement data analysis}
With the development of location-acquisition techniques, massive spatial trajectories are collected to keep track of the trajectories of various moving objects. Techniques have been proposed to process and mine trajectories for spatial knowledge~\cite{Zheng2015_trajectory}. In the field of visualization and visual analytics, spatial visualizations are specifically designed for time, location, spatiotemporal information and other properties in movement data~\cite{chen2015survey}. Wang et al.~\cite{wang2013visual} extract traffic jam propagation graphs to reveal underlying data patterns. Guo et al.~\cite{guo2011tripvista} and Zeng et al.~\cite{zeng2013visualizing} construct geographic regions and visually aggregate the in-between movements as flows. To discover route travel patterns, Lu et al.~\cite{lu2015trajrank} propose TrajRank to explore route travel behavior based on ranking. For multiple routes, Liu et al.~\cite{liu2011_routediversity} study the route diversity between locations and Lu et al.~\cite{Lu2017_multipleroute} explore the route choice behavior among multiple routes. These large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring. However, they prefer to discuss spatial feature of movements, neglecting the characteristics of the movers and the relationship between movement and movers. In this work, we focus on this to explore how to design visual analytics methods to relate demographic characteristics to spatial feature of movements.

\subsection{Geo-tagged Social Media Data Analysis}
In the presence of social media services, social media data with geo-tags are collected to track people's movements in their daily lives. As an analog of remote sensing data in social science research, geospatial big data has been proposed as social sensing ~\cite{liu2015social}. Hence, analyzing movement information along with rich text has become a popular research area in recent years. Krueger et al.~\cite{krueger2014visual} uses GPS and location-based service data to support the analysis of movement behaviors. Cao et al.~\cite{cao2012whisper} proposes \textit{Whisper} for tracing the pathways of tweets along a spatial hierarchical layout to investigate how information flows among multiple places. Some other researchers tend to infer real information, such as names, gender, and race, from social media data to form the image of social media users based on the demographic characteristics~\cite{peddinti2014internet} and analysis the impact of characteristics on urban human mobility patterns~\cite{luo2016explore}. These works infer thematic information from semantic texts. By analyzing the texts, these works explain what drives movement activities or what results from these activities. This work continues thematic research on movement data but focuses more on individual demographic characteristics. Since real information is not enforced in social media, incorrect inference is inevitable. The biases inherent in social media usage need to be assessed in social research and the deployment of social media data need to be evaluated in research applications~\cite{Longley2015, Paul2016_twitter} . Therefore, based on a census experiment, this work is able to analyze profile information directly to eliminate indirect data inferred from social media data as other related works do. Then an intuitive visualization is proposed to describe these characteristics of individuals.
\section{motivation}

@@

\textbf{Traveling Trips} Individuals can upload dynamic traveling trips (Fig. \ref{fig:app}(b)). Each trip requires information on the start/end location, start/end time, traveling purpose, and traveling mode. Locations are recorded by GPS modules in the phones. To encourage trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Fig. \ref{fig:app}(c)).

@@

The figure shows that, 51.2\% of the participating citizens are male and 48.8\% are female. This result is consistent with governmental statistics stating that 47\% of all citizens are female and 53\% are male\footnote{http://tjj.sz.gov.cn/zwgk/zfxxgkml/tjsj/tjgb/201804/t20180427\_11800902.htm}. The age collected covers a wide range, with ages between 18 and 45 dominating. There are also records pertaining to individuals below the age of 18 or above 70. According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aged 15-64 comprise 83.23\%, and the median age is 31.5. The age distribution in the collected data aligns with the fact that Shenzhen is a city where the majority of the population is young. From the distribution of education levels, ranging from low to high, technical colleges and universities dominate the samples at a 61\% occupancy rate. The majority get paid less than 200,000. Citizens with higher salaries are also reached in our census. Due to the lack of governmental statistics, we cannot verify that all the characteristics collected are consistent with all the citizens in Shenzhen. From the perspective of surveys, there is always inevitable bias inherent in fully representing the ground truth of the population. However, the preliminary statistical analysis shows the rich scope of the data, which is positive evidence of a relatively even sampling of the population of the city.

@@

The basic statistics related to movements are shown in Fig. \ref{fig:data_geometry}. Fig. ~\ref{fig:data_geometry}(a) visualizes the distribution of the trip quantity of each citizen. The distribution has a heavy-tail, which follows the trends of most human-related statistics. In Fig. ~\ref{fig:data_geometry}(b), the active traveling time (here, we take the start time as representative of the active time) follows the common knowledge about urban life. There are obvious morning and evening rush hours. Fig. ~\ref{fig:data_geometry}(c) shows the counts for different traveling purposes. Ninety-five percent of trips are tagged with a clear traveling purpose in the data. Thirty-three percent of trips are going home, and 37\% are going to work. In addition to this kind of routine travel, there are also substantial numbers of trips for other purposes such as going shopping and going the hospital. Fig. ~\ref{fig:data_geometry}(d) shows the spatial distribution of the origins and destinations. It is found that more dots are located in Futian and Nanshan Districts, the city's heart, than in the surrounding areas. This result is consistent with Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.

@@

\begin{figure}
    \centering
	  \subfloat[]{
       \includegraphics[width=86mm]{pictures/space1.eps}}
    \label{1a}\hfill
	  \subfloat[]{
        \includegraphics[width=86mm]{pictures/space2.eps}}
    \label{1b}\hfill
      \subfloat[]{
        \includegraphics[width=86mm]{pictures/space3.eps}}
    \label{1c}\\
\caption{Spatial visualization in 2.5D: (a) 2.5D spatial visualization with additional information encoded in z-axis; (b) detail slicing in 2.5D space; and (c) overview view.}
\label{fig:2.5D}
\end{figure}

Several interactions are integrated into the spatial view to alleviate the occlusion problem (\textit{C5}). The manipulation of the 2.5D view supports users with rotate, zoom, and pan operations, which is continuously flexible so that users can find a suitable observation point. In the cases where occlusion is inevitable, an interaction, namely, detail slicing (Fig. ~\ref{fig:2.5D}(b)), and an overview view (Fig. ~\ref{fig:2.5D}(c)) are developed. Detail slicing is an operation that places a cross-section in the 2.5D space to expose the TAZ inside. To contextualize the cross-section, the TAZs are visually adapted according to the intersection by ray casting. The TAZs in the foreground are hidden, the intersected TAZs are fully visualized, and those in the background are semi-transparent. The overview view shows all the TAZs in the form of a 2D plane. All the TAZs are tiled horizontally. The vertical axis indicates the height of each prism in each TAZ. It is for quickly sensing the distribution of encoded content with prism within the whole city.

@@

\begin{figure}[htb!]
 \centering
 \includegraphics[width=\columnwidth]{pictures/case1_3_new-eps-converted-to.pdf}
 \caption{Spatial distributions of "work", "home" and "other" for the four groups: (a) the 2.5D view; (b) three slices for detailed comparison; (c) the overview view of all the TAZs in the city.}
 \label{case13}
\end{figure}

>>>>

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{soul}

@@

Due to the multidimensional nature of demographic characteristics and the spatial diversity of movements, it is challenging to explore, analyze and express the relationship between these parameters. In recent decades, the power of visual analytics in urban problems has been recognized and developed well~\cite{wang2013visual, zeng2013visualizing}. The presence of social media applications fuels spatial analysis with rich semantic texts, so researchers can explore the thematic meaning of the movement behaviors, such as events~\cite{chen2017map} and topics~\cite{bosch2013scatterblogs2}. \hl{These works essentially contribute to deepening the contextual understanding of movement activities. Some works dive deep and infer individual characteristics from social media profiles}~\cite{peddinti2014internet} \hl{to better describe the semantics of movement behavior. However, due to the limited exposure of personal information, there is still a research gap between understanding the movement behavior and underlying characteristics of movers.}

@@

\subsection{Movement data analysis}
With the development of location-acquisition techniques, massive spatial trajectories are collected to keep track of the trajectories of various moving objects. Techniques have been proposed to process and mine trajectories for spatial knowledge~\cite{Zheng2015_trajectory}. In the field of visualization and visual analytics, spatial visualizations are specifically designed for time, location, spatiotemporal information and other properties in movement data~\cite{chen2015survey}. Wang et al.~\cite{wang2013visual} extract traffic jam propagation graphs to reveal underlying data patterns. Guo et al.~\cite{guo2011tripvista} and Zeng et al.~\cite{zeng2013visualizing} construct geographic regions and visually aggregate the in-between movements as flows. To discover route travel patterns, Lu et al.~\cite{lu2015trajrank} propose TrajRank to explore route travel behavior based on ranking. For multiple routes, Liu et al.~\cite{liu2011_routediversity} study the route diversity between locations and Lu et al.~\cite{Lu2017_multipleroute} explore the route choice behavior among multiple routes. These large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring. \hl{However, they prefer to discuss spatial feature of movements, neglecting the characteristics of the movers and the relationship between movement and movers. In this work, we focus on this to explore how to design visual analytics methods to relate demographic characteristics to spatial feature of movements.}

\subsection{Geo-tagged Social Media Data Analysis}
In the presence of social media services, social media data with geo-tags are collected to track people's movements in their daily lives. As an analog of remote sensing data in social science research, geospatial big data has been proposed as social sensing ~\cite{liu2015social}. Hence, analyzing movement information along with rich text has become a popular research area in recent years. Krueger et al.~\cite{krueger2014visual} uses GPS and location-based service data to support the analysis of movement behaviors. Cao et al.~\cite{cao2012whisper} proposes \textit{Whisper} for tracing the pathways of tweets along a spatial hierarchical layout to investigate how information flows among multiple places. Some other researchers tend to infer real information, such as names, gender, and race, from social media data to form the image of social media users based on the demographic characteristics~\cite{peddinti2014internet} and analysis the impact of characteristics on urban human mobility patterns~\cite{luo2016explore}. These works infer thematic information from semantic texts. \hl{By analyzing the texts, these works explain what drives movement activities or what results from these activities. This work continues thematic research on movement data but focuses more on individual demographic characteristics.} Since real information is not enforced in social media, incorrect inference is inevitable. The biases inherent in social media usage need to be assessed in social research and the deployment of social media data need to be evaluated in research applications~\cite{Longley2015, Paul2016_twitter}. \hl{Therefore, based on a census experiment, this work is able to analyze profile information directly to eliminate indirect data inferred from social media data as other related works do. Then an intuitive visualization is proposed to describe these characteristics of individuals.}
\section{motivation}

@@

\textbf{Traveling Trips} Individuals can upload dynamic traveling trips (Fig. \ref{fig:app}(b)). Each trip requires information on the start/end location, start/end time, traveling purpose, and traveling mode. Locations are recorded by GPS modules in the phones. \hl{A credit system} (Fig. \ref{fig:app}(c)) \hl{is utilized to encourage participation. Individuals who have enough credits will obtain raffle tickets. There are three ways for credits: recommending friends to participate in the survey, filling personal information, and filling daily trips.}

@@

The figure shows that, 51.2\% of the participating citizens are male and 48.8\% are female. This result is consistent with governmental statistics stating that 47\% of all citizens are female and 53\% are male\footnote{http://tjj.sz.gov.cn/zwgk/zfxxgkml/tjsj/tjgb/201804/t20180427\_11800902.htm}. The age collected covers a wide range, with ages between 18 and 45 dominating. There are also records pertaining to individuals below the age of 18 or above 70. According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aged 15-64 comprise 83.23\%, and the median age is 31.5. The age distribution in the collected data aligns with the fact that Shenzhen is a city where the majority of the population is young. From the distribution of education levels, ranging from low to high, technical colleges and universities dominate the samples at a 61\% occupancy rate. The majority get paid less than 200,000. Citizens with higher salaries are also reached in our census. \hl{Due to the lack of governmental statistics, we cannot verify that all the characteristics collected are consistent with all the citizens in Shenzhen. From the perspective of surveys, there is always inevitable bias inherent in fully representing the ground truth of the population. However, the preliminary statistical analysis shows the rich scope of the data, which is positive evidence of a relatively even sampling of the population of the city.}

@@

The basic statistics related to movements are shown in Fig. \ref{fig:data_geometry}. Fig. ~\ref{fig:data_geometry}(a) visualizes the distribution of the trip quantity of each citizen. The distribution has a heavy-tail, which follows the trends of most human-related statistics. All trips are reported by the participants. \hl{To make sure the trips are available, we checked trips from temporal and spatial perspectives.} In Fig. ~\ref{fig:data_geometry}(b), the active traveling time (here, we take the start time as representative of the active time) follows the common knowledge about urban life. There are obvious morning and evening rush hours. Fig. ~\ref{fig:data_geometry}(c) shows the counts for different traveling purposes. Ninety-five percent of trips are tagged with a clear traveling purpose in the data. Thirty-three percent of trips are going home, and 37\% are going to work. In addition to this kind of routine travel, there are also substantial numbers of trips for other purposes such as going shopping and going the hospital. Fig. ~\ref{fig:data_geometry}(d) shows the spatial distribution of the origins and destinations. It is found that more dots are located in Futian and Nanshan Districts, the city's heart, than in the surrounding areas. This result is consistent with Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.

@@

\begin{figure}
    \centering
	  \subfloat[]{
       \includegraphics[width=86mm]{pictures/space1.eps}}
    \label{1a}\hfill
	  \subfloat[]{
        \includegraphics[width=86mm]{pictures/space2.eps}}
    \label{1b}\hfill
      \subfloat[]{
        \includegraphics[width=86mm]{pictures/space3.eps}}
    \label{1c}\\
\caption{Spatial visualization in 2.5D: (a) 2.5D spatial visualization with additional information encoded in z-axis; (b) detail slicing in 2.5D space; and \hl{(c) overview view.}}
\label{fig:2.5D}
\end{figure}

Several interactions are integrated into the spatial view to alleviate the occlusion problem (\textit{C5}). The manipulation of the 2.5D view supports users with rotate, zoom, and pan operations, which is continuously flexible so that users can find a suitable observation point. In the cases where occlusion is inevitable, an interaction, namely, detail slicing (Fig. ~\ref{fig:2.5D}(b)), and an overview view (Fig. ~\ref{fig:2.5D}(c)) are developed. Detail slicing is an operation that places a cross-section in the 2.5D space to expose the TAZ inside. To contextualize the cross-section, the TAZs are visually adapted according to the intersection by ray casting. The TAZs in the foreground are hidden, the intersected TAZs are fully visualized, and those in the background are semi-transparent. \hl{The overview view shows all the TAZs in the form of a 2D plane. All the TAZs are tiled horizontally. The vertical axis indicates the height of each prism in each TAZ. It is for quickly sensing the distribution of encoded content with prism within the whole city.}

@@

\begin{figure}[htb!]
 \centering
 \includegraphics[width=\columnwidth]{pictures/case1_3_new-eps-converted-to.pdf}
 \caption{Spatial distributions of "work", "home" and "other" for the four groups: (a) the 2.5D view; (b) three slices for detailed comparison; \hl{(c) the overview view of all the TAZs in the city.}}
 \label{case13}
\end{figure}

### 2020-01-18 ia/ia_vis_3d_final.tex
with yellow

\textbf{Traveling Trips} Individuals can upload dynamic traveling trips (Fig. \ref{fig:app}(b)). Each trip requires information on the start/end location, start/end time, traveling purpose, and traveling mode. Locations are recorded by GPS modules in the phones. To encourage trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Fig. \ref{fig:app}(c)).

@@

The basic statistics related to movements are shown in Fig. \ref{fig:data_geometry}. Fig. ~\ref{fig:data_geometry}(a) visualizes the distribution of the trip quantity of each citizen. The distribution has a heavy-tail, which follows the trends of most human-related statistics. In Fig. ~\ref{fig:data_geometry}(b), the active traveling time (here, we take the start time as representative of the active time) follows the common knowledge about urban life. There are obvious morning and evening rush hours. Fig. ~\ref{fig:data_geometry}(c) shows the counts for different traveling purposes. Ninety-five percent of trips are tagged with a clear traveling purpose in the data. Thirty-three percent of trips are going home, and 37\% are going to work. In addition to this kind of routine travel, there are also substantial numbers of trips for other purposes such as going shopping and going the hospital. Fig. ~\ref{fig:data_geometry}(d) shows the spatial distribution of the origins and destinations. It is found that more dots are located in Futian and Nanshan Districts, the city's heart, than in the surrounding areas. This result is consistent with Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.

>>>>

\textbf{Traveling Trips} Individuals can upload dynamic traveling trips (Fig. \ref{fig:app}(b)). Each trip requires information on the start/end location, start/end time, traveling purpose, and traveling mode. Locations are recorded by GPS modules in the phones. A credit system (Fig. \ref{fig:app}(c)) is utilized to encourage participation. Individuals who have enough credits will obtain raffle tickets. There are three ways for credits: recommending friends to participate in the survey, filling personal information, and filling daily trips.

@@

The basic statistics related to movements are shown in Fig. \ref{fig:data_geometry}. Fig. ~\ref{fig:data_geometry}(a) visualizes the distribution of the trip quantity of each citizen. The distribution has a heavy-tail, which follows the trends of most human-related statistics. All trips are reported by the participants. To make sure the trips are available, we checked trips from temporal and spatial perspectives. In Fig. ~\ref{fig:data_geometry}(b), the active traveling time (here, we take the start time as representative of the active time) follows the common knowledge about urban life. There are obvious morning and evening rush hours. Fig. ~\ref{fig:data_geometry}(c) shows the counts for different traveling purposes. Ninety-five percent of trips are tagged with a clear traveling purpose in the data. Thirty-three percent of trips are going home, and 37\% are going to work. In addition to this kind of routine travel, there are also substantial numbers of trips for other purposes such as going shopping and going the hospital. Fig. ~\ref{fig:data_geometry}(d) shows the spatial distribution of the origins and destinations. It is found that more dots are located in Futian and Nanshan Districts, the city's heart, than in the surrounding areas. This result is consistent with Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.
